---
title: "convert csv to markdown table"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

This code is used to convert csv formated data into markdown table. There are websites and numerous tools providing similar service, but the websites I tried didn't recognize quote correctly. Using R will have more control over the format, and the clipboard intergration make the workflow smoother.

```{r libraries}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(knitr, data.table, clipr)
```

To use the code, first run the libraries code chunk, then copy the csv data into clipboard, run the code chunk below, the converted markdown table will be put into clipboard.

```{r code}
# clipr can read clipboard in windows/mac/linux
lines <- read_clip()
paste0(lines, collapse = "\n")
# getting regular data frame so we can use the matrix indexing in next line
df <- fread(paste0(lines, collapse = "\n"), na.strings = NULL, data.table = FALSE)
# we don't want to print NA in table since the actual data don't have NA returned
df[is.na(df)] <- ""
write_clip(kable(df, format = "markdown"))
```

